|

### 2019-11-20 analysis/paper/paper.Rmd
Minor formatting and figure fixes
More formatting tweaks for DOCX export

  - Alexey N. Shiklomanov
  - Ben Bond-Lamberty
  - Jeff Atkins
  - Christopher M. Gough
date: "`r format(Sys.time(), '%d %B, %Y')`"

@@

@@

pgbreak <- function() {
  if (grepl("docx", out_format)) {
    return("##### pagebreak")
  } else if (is_latex_output()) {
    return("\\newline")
  }
}

@@

The official ED-2.2 source code is available at https://github.com/EDmodel/ED2, and the exact version used in this study (which includes minor revisions to accommodate the requirements of this study) can be obtained at https://github.com/ashiklom/ED2/tree/b048950971e91699b78fc566df133caf977fda32.

@@

### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies:

```{r colophon, cache = FALSE}
# which R packages and versions?
devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? You may need to change the path value
# if your Rmd is not in analysis/paper/
git2r::repository(here::here())
```

View this project on GitHub in repository [ashiklom/fortebaseline](https://github.com/ashiklom/fortebaseline)
(this manuscript file is in [`analysis/paper/paper.Rmd`](https://github.com/ashiklom/fortebaseline/blob/master/analysis/paper/paper.Rmd))
and in Open Science Framework (OSF) at https://osf.io/dznuf/ .

>>>>

  - Alexey N. Shiklomanov$^{a *}$, Ben Bond-Lamberty$^a$, Jeffrey Atkins$^b$, Christopher M. Gough$^b$
  - $^a$ *Joint Global Change Research Institute, Pacific Northwest National Laboratory, College Park, MD, USA*; $^b$ *Department of Biology, Virginia Commonwealth University, Richmond, VA, USA*
  - "* Corresponding author: alexey.shiklomanov@pnnl.gov, (301) 314-6713; 5825 University Research Ct, Suite 3500, College Park, MD 20740"

@@

  **Abstract**:

@@

pgbreak <- function() {
  if (grepl("docx", out_format)) {
    return("##### pagebreak")
  } else if (is_latex_output()) {
    return("\\newpage")
  }
}

@@

The official ED-2.2 source code is available at https://github.com/EDmodel/ED2, and the exact version used in this study (which includes minor revisions to accommodate the requirements of this study) can be obtained at https://github.com/ashiklom/ED2/tree/b048950.

@@
